---
title: "Yonsei Internship Summer 2021"
author: "Sung Bum Ahn"
date: "3/10/2021"
output: html_document
---
```{r setup, include=FALSE}
# Do not modify this chunk.
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.retina = 2)
```

```{r}
# Load the necessary packages
library(tidyverse)
library(pdxTrees)
library(dplyr)
library(infer)
library(broom)
```

We are going to use data from the `pdxTrees` package. In particular, we will use the dataset called `four_parks` that I created below.

Make sure to run the following R chunk.

```{r}
# Grab trees near Reed
four_parks <- get_pdxTrees_parks(park = 
                                  c("Brooklyn Park",
                                          "Kenilworth Park",
                                          "Eastmoreland Garden",
                                          "Berkeley Park"))

#Remove trees with no functional type
four_parks <- drop_na(four_parks, Functional_Type)
```


A. Low difficulty questions


a. Create a bar plot of `park`.

Answer.
```{r}
# Bar plot
ggplot(data = four_parks, mapping = aes(x = Park)) +
  geom_bar()
  
```

b. 
```{r}

```



c. Tally the condition of trees in these four parks. Tally them accordingly and print only Park, Condition and n on a table.

```{r}
four_parks %>% 
  group_by(Park, Condition) %>% 
  tally()
```

B. Medium difficulty questions

a. Find the tallest tree within the park, and give its tree height, common name, date of data collected (Inventory Date), and park name. 

```{r}
# Tallest tree data frame
tallest <- four_parks %>%
  filter(Tree_Height == max(Tree_Height)) %>%
  select(Tree_Height, Common_Name, Inventory_Date, Park)
# Print wrangled data frame
tallest
```

b. Generate a boxplot that shows the tree heights by park. Make sure to calculate and include the mean of the tree height rounded to the tenth place on the graph. 

```{r}
means <- aggregate(Tree_Height ~  Park, four_parks, mean) 

ggplot(data = four_parks, mapping = aes(x = Park, y= Tree_Height)) +
  geom_boxplot()  +
  geom_text(data = means, aes(label = round(Tree_Height, 1), y = Tree_Height + 0.1)) 
            
```

c.Generate a bootstrap distribution with Tree_Height and DBH (Diameter at Breast Height). Drop any NA values. Have repetitions of bootstrapping at 1000.
```{r}
bootstrap_dist <- four_parks %>% 
  drop_na(Tree_Height, DBH) %>% 
  specify(Tree_Height ~ DBH) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "correlation")
bootstrap_dist
```



C. Hard difficulty questions
a. Using the 'four_parks' dataset, create a dataset called 'top3_park_op' with the two parks with the most “Douglas-Fir” trees. After this, change the name of “Douglas-Fir” to “Oregon Pine”. Do not remove n.  You will be assessed on the accuracy of “top3_park_op” data set.

```{r}
top2_park_op <- four_parks %>%
  group_by(Park) %>% 
  count(Common_Name) %>% 
  filter(Common_Name == "Douglas-Fir") %>% 
  arrange(desc(n)) %>%
  ungroup() %>% 
  slice_head(n = 2) %>% 
  mutate(Common_Name = case_when(Common_Name == "Douglas-Fir" ~ "Oregon Pine",
                                 TRUE ~ as.character(Common_Name)))
```


b. Compute the ANOVA test statistic ($F_o$) for Tree_Height by Park in four_parks. and also produce an ANOVA table using 'aov()'. Now generate a simulation-based null distribution of the test statistics for Tree Heights, round up the intercept to the nearest tenth place. 

```{r}
th_four_parks <- four_parks %>%
  specify(Tree_Height ~ Park) %>%
  calculate(stat = "F") 
th_four_parks

mod <- aov(Tree_Height ~ Park, data = four_parks)
tidy(mod)

null_dist_four_parks <- four_parks %>%
  specify(Tree_Height ~ Park) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "F") 
null_dist_four_parks

visualize(null_dist_four_parks) +
  geom_vline(xintercept= 6.29)
```

c. Want to display diff geom for diff dataset on same graph, bootstrap to measure a center. Single sample and resample and for each sample compute the mean and compute the median and plot the histogram and historgams are labels by a legend. 
```{r}


```